Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-01-28 Manuscript/FLPhish(Trans).tex
Performance Comparison with Different Distributions Update

    \subsubsection{\ul{Performance Comparison with Different Distributions}} We evaluate our FLPhish(weight) under the experiment setting where the Byzantine client portion is a fixed value of 0.5 and distribution imbalance value $q$ is different across the experiments. The experiment results are shown in Fig. \ref{fig_table_imbalances_untargeted}. We can observe that both the FLPhish($\tau$=0.1,0.2,0.5) and FLPhish(weight) outperform baseline until the imbalance degree $q$ reaches 0.8. The imbalance degree $q$ of 0.8 means that the distribution of data becomes extremely non-IID. The performance of the FLPhish($\tau$=0.5) rapidly falls in this case. When facing the distribution of imbalance degree $q=0.8$, each client performs badly, bringing a decline to its reputation. The rise of imbalance degree brings an explosive decline in the global model's accuracy. The accuracy of the global model under the FLPhish($\tau$=0.5) stays to be 0.1 in the whole learning process. It means that the FLPhish($\tau$=0.5) identifies all the clients as Byzantine clients, making the aggregation process invalid. We can see that the FLPhish($\tau$=0.2) outperforms others. When the distribution becomes non-IID, the threshold of FLPhish($\tau$) should be set to a lower value to avoid a high false-negative rate. In the experiment of MNIST, it should be set to 0.2. Meanwhile, the performance of FLPhish(weight) remains stable under different imbalance degrees.

>>>>

    \subsubsection{\ul{Performance Comparison with Different Distributions}} We test our FLPhish(weight) in an experiment environment with a fixed Byzantine client fraction of 0.5 and a variable distribution imbalance value $q$ across tests. The experiment results are shown in Fig. \ref{fig_table_imbalances_untargeted}. We can see that both FLPhish($\tau$=0.1,0.2,0.5) and FLPhish(weight) outperform other schemes. When the imbalance degree $q$ reaches 0.8, the distribution of data becomes very non-IID. In this situation, the FLPhish($\tau$=0.5)'s performance progressively deteriorates. When confronted with a distribution with an imbalance degree of $q=0.8$, each client performs poorly, resulting in a loss of reputation. The accuracy of the global model declines sharply as the degree of imbalance rises. Throughout the learning phase, the accuracy of the global model under FLPhish($\tau$=0.5) remains at 0.1. It means that FLPhish($\tau$=0.5) considers all clients to be Byzantine, thus invalidating the aggregation process. As can be seen, the FLPhish($\tau$=0.2) outperforms the FLPhish($\tau$=0.1,0.5). To avoid a high false-negative rate, the threshold $\tau$ of FLPhish($\tau$) should be set to a lower value when the distribution becomes non-IID. It should be set to 0.2 in the MNIST experiment. Meanwhile, FLPhish(weight) maintains its performance under varying degrees of imbalance.
